### 2021-08-23 plos_latex_template.tex
RJ: edits to the conclusion

The ten rules stated here can be adapted depending on the conference format and settings. From our own experience, we are aware that enforcing these rules requires a tremendous amount of work that is generally not compensated financially or otherwise. However, the rewards from these suggested best practices will provide a healthier, stronger, and more inclusive community, empowering historically marginalized people and learning from them, thereby increasing the overall quality of the conference. Since these are early days and accessibility is not as widespread as it should be, the process might seem exacting. Hopefully, if more conferences and domains employ these techniques, the process will get more streamlined, straightforward, and mainstream to adapt with minimal overhead. After all, the strength of any community lies in its ability to be adaptive, inclusive, and accessible.

>>>>

The ten rules stated here can be adapted depending on the conference format and settings. From our own experience, we are aware that enforcing these rules requires a tremendous amount of work. We engaged in most of these practices, and others, like having an explicit payment category for postdocs or paying the whole organizing team, we learned them too late, so we share them here as part of our learning. 
Since accessibility and inclusiveness are not as widespread as it should be, the process might seem exacting. But this is where the power of communities and individuals reside. If more conferences and domains employ these techniques, the process will get more streamlined, straightforward, and mainstream to adapt with minimal overhead. And we will make a change towards healthier, stronger, and more inclusive communities, empowering historically marginalized people and learning from them, thereby increasing the overall quality of our conferences.%After all, the strength of any community lies in its ability to be adaptive, inclusive, and accessible.
